Convergence rate of MAP estimates \\ for the exponential family

### 2021-10-29 aistats.tex
No break bibliography
Add acknowledgements

\nocite{dragomir2021optimal}
\newpage
\bibliographystyle{apalike}
\bibliography{references}

>>>>

\subsubsection*{Acknowledgments}
We express our gratitude to Reza Babanezhad, Radu Dragomir and Hadrien Hendrikx for their insights on stochastic mirror descent. 
This work was partially supported by the Canada CIFAR AI Chair Program. 
Simon Lacoste-Julien is a CIFAR Associate Fellow in the Learning in Machines \& Brains program.

\bibliographystyle{apalike}
\bibliography{references}
